working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-03-03 Manuscript_draft/Manuscript_draft.Rmd
edits

**Table 1**
```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
library(kableExtra)
Family <- c(rep("Brassicaceae",4), rep("Convolvulaceae", 2), rep("Solanaceae",4))

@@

>>>>

\newpage
**Table 1**
```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
library(kableExtra)
Family <- c(rep("Brassicaceae",4), rep("Convolvulaceae", 2), rep("Solanaceae",4))

@@

\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.width=6,fig.height=5, fig.cap="A"}
library(ape)
library(phytools)
pollen_tree=read.tree("Data/pollen_tree.nwk")
plot(pollen_tree)
add.scale.bar(x=0, y=1, length = 0.01)
```

### 2019-03-03 Manuscript_draft/Manuscript_draft.tex
some edits, error to knit, dont know why
edits

\textbf{Table 1}

@@

@@

Results of hand cross-pollination, self hand-pollination, natural
selfing and apomixis are presented in \textbf{Figure 1} (see appendix 1
for table with values). Heterospecific pollen reduced seet set
significatively with the 50-50\% heterospecific pollen treatments for
65\% of the pairwise interactions p\textless{}0.05.

@@

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-2-1.pdf}
\caption{Barplot with the different treatments that provide information
of the reproductive biology of the ten species. The y axis is the
proportion of ovules converted to seed in percentage. The different
treatments (N=10) which are presented in the legend are, hand cross
pollination, hand self pollination, natural selfing and apomixis. More
information about these treatments can be found in Methods and
Appendices.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-3-1.pdf}
\caption{Effect sizes for the 10 different species. The different
families appear with different colours, when a species was focal was
coloured differently from its family.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-4-1.pdf}
\caption{The effect of heterospecific pollen (scaled see set) is
represented in function of the compatibility system (self/cross*100) for
the the different species. Each coulored dot represents the interaction
of a focal species with a different pollen donor.}
\end{figure}

@@

\includegraphics{output/figures/unnamed-chunk-6-1.pdf}
\includegraphics{output/figures/unnamed-chunk-6-2.pdf}
\includegraphics{output/figures/unnamed-chunk-6-3.pdf}

>>>>

\newpage
*

*Table 1**

@@

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-2-1.pdf}
\caption{A}
\end{figure}

@@

Results of hand cross-pollination, self hand-pollination, natural
selfing and apomixis are presented in \textbf{Figure 1} (see appendix 1
for table with values). Heterospecific pollen reduced seet set
significatively with the 50-50\% heterospecific pollen treatments for
65\% of the pairwise interactions p\textless{}0.05. Moreover, effect
sizes differ across species, see \textbf{Figure 2} where species like
\emph{S. lycopersicum} had a large effect size and other's like \emph{E.
sativa} a small or null effect size.

@@

\begin{figure}

{\centering \includegraphics{output/figures/unnamed-chunk-3-1}

}

\caption{Barplot with the different treatments that provide information of the reproductive biology of the ten species. The y axis is the proportion of ovules converted to seed in percentage. The different treatments (N=10) which are presented in the legend are, hand cross pollination, hand self pollination, natural selfing and apomixis. More information about these treatments can be found in Methods and Appendices.}\label{fig:unnamed-chunk-3}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-4-1.pdf}
\caption{Effect sizes for the 10 different species. The different
families appear with different colours, when a species was focal was
coloured differently from its family.}
\end{figure}

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-5-1.pdf}
\caption{A}
\end{figure}

Maybe for this plot I have to do hedges'g instead of cohean because of
different sample sizes when I group the treatments per family. Check

@@

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-6-1.pdf}
\caption{The effect of heterospecific pollen (scaled see set) is
represented in function of the compatibility system (self/cross*100) for
the the different species. Each coulored dot represents the interaction
of a focal species with a different pollen donor.}
\end{figure}

@@

\includegraphics{output/figures/unnamed-chunk-8-1.pdf}
\includegraphics{output/figures/unnamed-chunk-8-2.pdf}
\includegraphics{output/figures/unnamed-chunk-8-3.pdf}
